---
title: "Intermediate_Stats_Report"
author: "Varnith"
date: "20 December 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Importing the data into R

```{r}
Final_Train_data<-read.csv("E:/Rutgers/1st-Sem/Project_Intermediate/Data/Final_Train_data.csv",stringsAsFactors = FALSE)


blog_test<-read.csv("C:/Users/Varnith/Desktop/Blog_Test_Data.csv",stringsAsFactors = FALSE)

View(blog_test)

```


**In this step we have read the data into R.The two datasets are train and test data.The Final train data corresponds to Train and blog_test is test data on which we predict.**


##Linear Regression-Basic
```{r}

Final_Train_data_basic <- Final_Train_data[c(1:59,277)]

set.seed(123)
Final_Sample_data_basic<-Final_Train_data_basic[sample(nrow(Final_Train_data_basic), 10000), ]


blog_test_basic<-blog_test[,c(1:59,277)]


lm_basic_normal = lm(((Target)) ~ .,data= Final_Sample_data_basic)
summary(lm_basic_normal)

# stepwise BIC FOR normal_basic

lm1.step_basic_normal=step(lm_basic_normal, scope=list(lower=~1,
                                             upper=~.,direction='both', 
                                             data= Final_Sample_data_basic, 
                                             trace=TRUE, 
                                             k=log(nrow(Final_Sample_data_basic)), 
                                             criterion = 'BIC')) 

summary(lm1.step_basic_normal)

blog_test$lm_basic<-predict(lm1.step_basic_normal,blog_test_basic ,type="response")





```

**In this step run linear regression stepwise on random sample on basic features only.**

##Linear Regression-Basic+Parent
```{r}


Final_Train_data1 <- Final_Train_data[c(1:59,274:277)]
set.seed(123)
Final_Sample_data1<-Final_Train_data1[sample(nrow(Final_Train_data1), 10000), ]

blog_test_basic_parent<-blog_test[,c(1:59,274:277)]


lm2 = lm(((Target)) ~ .,data= Final_Sample_data1)
summary(lm2)

lm1.step2=step(lm2, scope=list(lower=~1,
                                  upper=~.,direction='both', 
                                  data= Final_Sample_data1, 
                                  trace=TRUE, 
                                  k=log(nrow(Final_Sample_data1)), 
                                  criterion = 'BIC')) 


summary(lm1.step2)



blog_test$lm_parent<-predict(lm1.step2,blog_test_basic_parent ,type="response")


```


**In this step run linear regression stepwise on random sample on basic+Parent features only.**

##Linear Regression-Basic+Weekday
```{r}

Final_Train_data_basic_weekday <- Final_Train_data[c(1:59,260:273, 277)]
set.seed(123)
Final_Train_data_basic_weekday<-Final_Train_data_basic_weekday[sample(nrow(Final_Train_data_basic_weekday), 10000), ]

blog_test_basic_weekday<-blog_test[,c(1:59,260:273, 277)]


lm_basic_weekday_normal = lm(((Target)) ~ .,data= Final_Train_data_basic_weekday)
summary(lm_basic_weekday_normal)


lm1.stepwise_basic_weekday_normal = step(lm_basic_weekday_normal, scope=list(lower=~1,
                                                                  upper=~.,direction='both', 
                                                                  data= Final_Train_data_basic_weekday, 
                                                                  trace=TRUE, 
                                                                  k=log(nrow(Final_Train_data_basic_weekday)), 
                                                                  criterion = 'BIC'))

summary(lm1.stepwise_basic_weekday_normal)





blog_test$lm_weekday<-predict(lm1.stepwise_basic_weekday_normal,blog_test_basic_weekday ,type="response")



```


**In this step run linear regression stepwise on random sample on basic+weekday features only.**

##Linear Regression-All Features
```{r}


set.seed(123)
Final_Train_data_sample<-Final_Train_data[sample(nrow(Final_Train_data), 10000), ]

lm_mod = lm(((Target)) ~ No_.Com_bstime_51+
No_cmnts_last_24_hrs+
No_commn_btw_T1_T2+
No_cmnts_1st_24_b4_basetime+
No_Links_last_24_hrs+
Time_Btw_Blog_Base+
Word_7+
Word_10+
Word_15+
Word_23+
Word_26+
Word_29+
Word_30+
Word_43+
Word_48+
Word_85+
Word_98+
Word_109+
Word_113+
Word_122+
Word_132+
Word_135+
Word_140+
Word_148+
Word_160+
Word_171+
Word_176+
Word_180+
Word_183+
Word_192+
Word_193+
Word_195+
Tuesday_Basetime+
Thursday_Basetime+
Friday_Basetime+
Saturday_Basetime+
Avg_Com_Par,data= Final_Train_data_sample)
summary(lm_mod)


lm1.stepwise_all_features = step(lm_mod, scope=list(lower=~1,upper=~No_.Com_bstime_51+
No_cmnts_last_24_hrs+
No_commn_btw_T1_T2+
No_cmnts_1st_24_b4_basetime+
No_Links_last_24_hrs+
Time_Btw_Blog_Base+
Word_7+
Word_10+
Word_15+
Word_23+
Word_26+
Word_29+
Word_30+
Word_43+
Word_48+
Word_85+
Word_98+
Word_109+
Word_113+
Word_122+
Word_132+
Word_135+
Word_140+
Word_148+
Word_160+
Word_171+
Word_176+
Word_180+
Word_183+
Word_192+
Word_193+
Word_195+
Tuesday_Basetime+
Thursday_Basetime+
Friday_Basetime+
Saturday_Basetime+
Avg_Com_Par
,direction='both', data= Final_Train_data_sample, trace=TRUE,k=log(nrow(Final_Train_data_sample)),criterion = 'BIC'))



summary(lm1.stepwise_all_features)


blog_test$lm_all_features<-predict(lm1.stepwise_all_features,blog_test[,1:277] ,type="response")



```


** While running the regression for linear model we removed the insignifcant variables depending on the p-Value and re ran a stepwise regression method.**


##Basic Features-Poisson Regression

```{r}


set.seed(123)
Final_Train_Continous<-Final_Train_data[,c(1:59,277)]

Final_Sample_data<-Final_Train_Continous[sample(nrow(Final_Train_Continous), 10000,replace = F), ]

blog_test_basic<-blog_test[,c(1:59,277)]



poisson_glm<-glm(formula=Final_Sample_data$Target~1+.,family=poisson(link=log),data=Final_Sample_data)


poisson_glm_step_basic<-step(poisson_glm,scope=list(lower=~1, upper=~.),direction='both', data= Final_Sample_data, trace=TRUE, k=log(nrow(Final_Sample_data)), criterion = 'BIC')

summary(poisson_glm_step_basic)

blog_test$poisson_basic_response<-predict(poisson_glm_step_basic,blog_test_basic,type="response")


```

**In this step we have run the poisson regression on basic features of the data on a random sample of 10,000 and also predicted on blog test data.**



##Basic + Parent Features-Poisson Regression

```{r}

set.seed(123)

Final_Train_Continous<-Final_Train_data[,c(1:59,274:277)]

Final_Sample_data<-Final_Train_Continous[sample(nrow(Final_Train_Continous), 10000,replace = F), ]


blog_test_basic_parent<-blog_test[,c(1:59,274:277)]

poisson_glm<-glm(formula=Final_Sample_data$Target~1+.,family=poisson(link=log),data=Final_Sample_data)
summary(poisson_glm)


poisson_glm_step_parent<-step(poisson_glm,scope=list(lower=~1, upper=~.),direction='both', data= Final_Sample_data, trace=TRUE, k=log(nrow(Final_Sample_data)), criterion = 'BIC')

summary(poisson_glm_step_parent)

blog_test$Poisson_Basic_Parent_Response<-predict(poisson_glm_step_parent,blog_test_basic_parent,type="response")



```

**In this step we have run the poisson regression on basic + parent features of the data on a random sample of 10,000 and also predicted on blog test data.**



##Basic+ Weekday Features-Poisson Regression

```{r}


set.seed(123)
Final_Train_Continous<-Final_Train_data[,c(1:59,260:273,277)]

Final_Sample_data<-Final_Train_Continous[sample(nrow(Final_Train_Continous), 10000,replace = F), ]


blog_test_basic_weekday<-blog_test[,c(1:59,260:273,277)]

poisson_glm<-glm(formula=Final_Sample_data$Target~1+.,family=poisson(link=log),data=Final_Sample_data)


poisson_glm_step<-step(poisson_glm,scope=list(lower=~1, upper=~.),direction='both', data= Final_Sample_data, trace=TRUE, k=log(nrow(Final_Sample_data)), criterion = 'BIC')

summary(poisson_glm_step)

blog_test$Predict_Basic_Weekday<-predict(poisson_glm_step,blog_test_basic_weekday,type="response")






```

**In this step we have run the poisson regression on basic + weekday features of the data on a random sample of 10,000 and also predicted on blog test data.**




##All Features-Poisson Regression

```{r}



set.seed(123)

Final_Sample_data<-Final_Train_data[sample(nrow(Final_Train_data), 10000,replace = F), ]



poisson_glm<-glm(formula=Final_Sample_data$Target~1+Average_No_.Com_bstime_51.+
standard.deviation_No_.Com_bstime_51.+
min_No_.Com_bstime_51.+
max_No_.Com_bstime_51.+
median._No_.Com_bstime_51.+
Average_No_cmnts_last_24_hrs+
standard.deviation_No_cmnts_last_24_hrs+
min_No_cmnts_last_24_hrs+
max_No_cmnts_last_24_hrs+
median._No_cmnts_last_24_hrs+
Average_No_commn_btw_T1_T2..+
X.max_No_commn_btw_T1_T2..+
X.median._No_commn_btw_T1_T2..+
Average_No_cmnts_1st_24_b4_basetime..+
X.standard.deviation_No_cmnts_1st_24_b4_basetime..+
X.max_No_cmnts_1st_24_b4_basetime..+
X.median._No_cmnts_1st_24_b4_basetime..+
Average_Diff_Attribute_52_53..+
X.standard.deviation_Diff_Attribute_52_53..+
X.min_Diff_Attribute_52_53..+
X.max_Diff_Attribute_52_53..+
X.median._Diff_Attribute_52_53..+
Average_No_.Link_bstime_51.+
standard.deviation_No_.Link_bstime_51.+
min_No_.Link_bstime_51.+
max_No_.Link_bstime_51.+
median._No_.Link_bstime_51.+
Average_No_Link_last_24_hrs+
standard.deviation_No_Link_last_24_hrs+
max_No_Link_last_24_hrs+
median._No_Link_last_24_hrs+
Average_No_Link_btw_T1_T2..+
X.standard.deviation_No_Link_btw_T1_T2..+
X.median._No_Link_btw_T1_T2..+
Average_No_Link_1st_24_b4_basetime..+
X.max_No_Link_1st_24_b4_basetime..+
X.median._No_Link_1st_24_b4_basetime..+
Average_Diff_Attribute_52_53_link.+
X.standard.deviation_Diff_Attribute_52_53_link.+
X.min_Diff_Attribute_52_53_link..+
X.median._Diff_Attribute_52_53_link.+
No_.Com_bstime_51+
No_cmnts_last_24_hrs+
No_commn_btw_T1_T2+
No_cmnts_1st_24_b4_basetime+
No_.Links_bstime_51+
No_Links_last_24_hrs+
No_Links_btw_T1_T2+
No_Links_1st_24_b4_basetime+
Time_Btw_Blog_Base+
Len_Blog_Post+
Word_1+
Word_2+
Word_5+
Word_6+
Word_7+
Word_8+
Word_9+
Word_12+
Word_13+
Word_16+
Word_17+
Word_20+
Word_21+
Word_23+
Word_24+
Word_30+
Word_31+
Word_34+
Word_36+
Word_37+
Word_38+
Word_39+
Word_41+
Word_42+
Word_43+
Word_44+
Word_45+
Word_46+
Word_48+
Word_50+
Word_52+
Word_54+
Word_55+
Word_56+
Word_57+
Word_59+
Word_60+
Word_61+
Word_64+
Word_65+
Word_66+
Word_72+
Word_73+
Word_74+
Word_75+
Word_76+
Word_77+
Word_78+
Word_79+
Word_80+
Word_82+
Word_83+
Word_84+
Word_85+
Word_89+
Word_90+
Word_91+
Word_92+
Word_95+
Word_96+
Word_97+
Word_100+
Word_101+
Word_102+
Word_103+
Word_105+
Word_108+
Word_112+
Word_113+
Word_114+
Word_118+
Word_119+
Word_120+
Word_121+
Word_122+
Word_123+
Word_124+
Word_127+
Word_129+
Word_131+
Word_132+
Word_133+
Word_134+
Word_137+
Word_139+
Word_140+
Word_143+
Word_144+
Word_145+
Word_147+
Word_148+
Word_151+
Word_153+
Word_154+
Word_155+
Word_156+
Word_157+
Word_158+
Word_159+
Word_160+
Word_162+
Word_163+
Word_164+
Word_165+
Word_166+
Word_167+
Word_168+
Word_169+
Word_170+
Word_171+
Word_172+
Word_173+
Word_175+
Word_177+
Word_178+
Word_179+
Word_180+
Word_183+
Word_184+
Word_185+
Word_186+
Word_187+
Word_189+
Word_190+
Word_192+
Word_193+
Word_194+
Word_196+
Word_198+
Word_199+
Wednesday_Basetime+
Thursday_Basetime+
Friday_Basetime+
Saturday_Basetime+
Mon_BlogPost+
Tue_BlogPost+
Wed_BlogPost+
Thur_BlogPost+
Fri_BlogPost+
Sat_BlogPost+
No_Parent_Page+
Max_Com_Par+
Avg_Com_Par,family=poisson(link=log),data=Final_Sample_data)


summary(poisson_glm)


poisson_glm_step<-step(poisson_glm,scope=list(lower=~1, upper=~Average_No_.Com_bstime_51.+
standard.deviation_No_.Com_bstime_51.+
min_No_.Com_bstime_51.+
max_No_.Com_bstime_51.+
median._No_.Com_bstime_51.+
Average_No_cmnts_last_24_hrs+
standard.deviation_No_cmnts_last_24_hrs+
min_No_cmnts_last_24_hrs+
max_No_cmnts_last_24_hrs+
median._No_cmnts_last_24_hrs+
Average_No_commn_btw_T1_T2..+
X.max_No_commn_btw_T1_T2..+
X.median._No_commn_btw_T1_T2..+
Average_No_cmnts_1st_24_b4_basetime..+
X.standard.deviation_No_cmnts_1st_24_b4_basetime..+
X.max_No_cmnts_1st_24_b4_basetime..+
X.median._No_cmnts_1st_24_b4_basetime..+
Average_Diff_Attribute_52_53..+
X.standard.deviation_Diff_Attribute_52_53..+
X.min_Diff_Attribute_52_53..+
X.max_Diff_Attribute_52_53..+
X.median._Diff_Attribute_52_53..+
Average_No_.Link_bstime_51.+
standard.deviation_No_.Link_bstime_51.+
min_No_.Link_bstime_51.+
max_No_.Link_bstime_51.+
median._No_.Link_bstime_51.+
Average_No_Link_last_24_hrs+
standard.deviation_No_Link_last_24_hrs+
max_No_Link_last_24_hrs+
median._No_Link_last_24_hrs+
Average_No_Link_btw_T1_T2..+
X.standard.deviation_No_Link_btw_T1_T2..+
X.median._No_Link_btw_T1_T2..+
Average_No_Link_1st_24_b4_basetime..+
X.max_No_Link_1st_24_b4_basetime..+
X.median._No_Link_1st_24_b4_basetime..+
Average_Diff_Attribute_52_53_link.+
X.standard.deviation_Diff_Attribute_52_53_link.+
X.min_Diff_Attribute_52_53_link..+
X.median._Diff_Attribute_52_53_link.+
No_.Com_bstime_51+
No_cmnts_last_24_hrs+
No_commn_btw_T1_T2+
No_cmnts_1st_24_b4_basetime+
No_.Links_bstime_51+
No_Links_last_24_hrs+
No_Links_btw_T1_T2+
No_Links_1st_24_b4_basetime+
Time_Btw_Blog_Base+
Len_Blog_Post+
Word_1+
Word_2+
Word_5+
Word_6+
Word_7+
Word_8+
Word_9+
Word_12+
Word_13+
Word_16+
Word_17+
Word_20+
Word_21+
Word_23+
Word_24+
Word_30+
Word_31+
Word_34+
Word_36+
Word_37+
Word_38+
Word_39+
Word_41+
Word_42+
Word_43+
Word_44+
Word_45+
Word_46+
Word_48+
Word_50+
Word_52+
Word_54+
Word_55+
Word_56+
Word_57+
Word_59+
Word_60+
Word_61+
Word_64+
Word_65+
Word_66+
Word_72+
Word_73+
Word_74+
Word_75+
Word_76+
Word_77+
Word_78+
Word_79+
Word_80+
Word_82+
Word_83+
Word_84+
Word_85+
Word_89+
Word_90+
Word_91+
Word_92+
Word_95+
Word_96+
Word_97+
Word_100+
Word_101+
Word_102+
Word_103+
Word_105+
Word_108+
Word_112+
Word_113+
Word_114+
Word_118+
Word_119+
Word_120+
Word_121+
Word_122+
Word_123+
Word_124+
Word_127+
Word_129+
Word_131+
Word_132+
Word_133+
Word_134+
Word_137+
Word_139+
Word_140+
Word_143+
Word_144+
Word_145+
Word_147+
Word_148+
Word_151+
Word_153+
Word_154+
Word_155+
Word_156+
Word_157+
Word_158+
Word_159+
Word_160+
Word_162+
Word_163+
Word_164+
Word_165+
Word_166+
Word_167+
Word_168+
Word_169+
Word_170+
Word_171+
Word_172+
Word_173+
Word_175+
Word_177+
Word_178+
Word_179+
Word_180+
Word_183+
Word_184+
Word_185+
Word_186+
Word_187+
Word_189+
Word_190+
Word_192+
Word_193+
Word_194+
Word_196+
Word_198+
Word_199+
Wednesday_Basetime+
Thursday_Basetime+
Friday_Basetime+
Saturday_Basetime+
Mon_BlogPost+
Tue_BlogPost+
Wed_BlogPost+
Thur_BlogPost+
Fri_BlogPost+
Sat_BlogPost+
No_Parent_Page+
Max_Com_Par+
Avg_Com_Par
),direction='both', data= Final_Sample_data, trace=TRUE, k=log(nrow(Final_Sample_data)), criterion = 'BIC')





blog_test$Predict_all_features<-predict(poisson_glm,blog_test[,1:277],type ="response")


write.csv(blog_test,"E:/Rutgers/1st-Sem/Project_Intermediate/blog_test2.csv")


```

**In this step we have run the poisson regression on all features.Due to the computation time taken on running stepwise regression,We have only kept the final significant variables in the model after stepwise selection method.First method involved removing variables which were insignificant that is having p value greater than .05 and then running stepwise selection method.**









